A Kochen-Specker system has at least 21 vertices\\ {\small (extended abstract)}

### 2014-04-14 main.tex
future research

With this method, we have decided the embeddability of every squarefree
graph with minimal vertex order three of 13 vertices of less.
In particular:
\begin{comp}
    Every squarefree graph of minimal vertex order three
    that is not 010-colorable
    of order less than or equal 20
    contains as a subgraph one of
    \begin{center}
        \includegraphics[width=120mm]{graphs/unemb-base-20.jpg}
    \end{center}
    which are unembeddable.  The left and middle graph
    are the only minimal unembeddable squarefree graph.
\end{comp}
For the first graph, we have proven directly that it is unembeddable.
See Proposition~\ref{prop:unemb-10-2}.
For the second graph, we also have a direct proof.

\section{Conclusion and future research}
TODO

>>>>

With this method, we have decided the embeddability of every squarefree
graph with minimal vertex order three of 13 vertices of less.
In particular:
\begin{comp}
    Every squarefree graph of minimal vertex order three
    that is not 010-colorable
    of order less than or equal to 20
    contains, as a subgraph, one of the following three graphs:
    \begin{center}
        \includegraphics[width=120mm]{graphs/unemb-base-20.jpg}
    \end{center}
    These three graphs are unembeddable.  The left and middle graph
    are the only minimal unembeddable squarefree graph.
\end{comp}
For the first graph, we have proven directly that it is unembeddable.
See Proposition~\ref{prop:unemb-10-2}.
For the second graph, we also have a similar direct proof. The third graph is shown to not be embeddable using our algorithm.

\section{Conclusion and future research}
At the time of writing, we are running a computation to find all possible KS graphs of order 22. We can then check if these graphs contain any of our found non embeddable subgraphs. We can use our method to check the embeddability of the graphs that have not been excluded. In theory, we can do this for all graphs up to order 31, or until we find an embeddable smaller graph. However, it might be that the amount of these graphs becomes too big. Even to an extend where they exceed even the number of particles in the universe.
